Phenotypic evolution is less constrained in complex food webs or Food-web complexity alters the fitness landscape of an insect herbivore

### 2018-09-20 ms_complexity_selection.Rmd
updated global tests of GLMMs

## Fit GLMMs
null_glmer <- glmer(gall_survival ~ 1 +
                      (1|Genotype/Plant_Position/Gall_Number),
                    data = gall_selection.df,
                    family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))

trait_glmer <- glmer(gall_survival ~ (sc.Diam + sc.log.Clutch + sc.log1p.Pref)^2 + #sc.Diam*sc.log.Clutch*sc.log1p.Pref + 
                      I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.log1p.Pref^2) +
                      (1|Genotype/Plant_Position/Gall_Number),
                    data = gall_selection.df,
                    family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))

foodweb_glmer <- glmer(gall_survival ~ Foodweb*(sc.Diam + sc.log.Clutch + sc.log1p.Pref)^2 +
                         Foodweb*(I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.log1p.Pref^2)) +
                         (1|Genotype/Plant_Position/Gall_Number),
                       data = gall_selection.df,
                       family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))

## Test for overdispersion
overdisp_fun(null_glmer)     # no evidence
overdisp_fun(trait_glmer)    # no evidence
overdisp_fun(foodweb_glmer)  # no evidence

## Test for multicollinearity
vif.mer(trait_glmer)
vif.mer(foodweb_glmer)

## Compare statistical summaries of each model
summary(null_glmer)
summary(trait_glmer)
summary(foodweb_glmer)

rsquared(trait_glmer, method="delta")
rsquared(foodweb_glmer, method="delta")

@@

# Overall, there is clear evidence that food-web treatment alters absolute fitness
anova(null_glmer, trait_glmer, foodweb_glmer, test = "Chisq")

## Parse out mechanisms of food-web effects ----
foodweb_glmer_beta <- glmer(gall_survival ~ Foodweb*(sc.Diam + sc.log.Clutch + sc.log1p.Pref) +
                         (1|Genotype/Plant_Position/Gall_Number),
                       data = gall_selection.df,
                       family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
test <- tidy(foodweb_glmer_beta, confint=T) %>%
  filter(term %in% c("(Intercept)","FoodwebSimple","sc.Diam","sc.log.Clutch","sc.log1p.Pref",
                     "FoodwebSimple:sc.Diam","FoodwebSimple:sc.log.Clutch","FoodwebSimple:sc.log1p.Pref")) %>%
  select(-group)
data.frame(term = test[,1], round(test[,-1],3))

# Use drop1 to test highest order effects and visreg to visualize the effects
# Use update to remove highest order effects from more complex models.

# Evidence that food-web treatment alters nonlinear selection acting on female preference. Appears to be evidence for disruptive selection in complex food web, but a lack of nonlinear selection in the simple food web.
drop1(foodweb_glmer, test="Chisq")
summary(foodweb_glmer)
visreg::visreg(foodweb_glmer, xvar="sc.log1p.Pref", by="Foodweb", scale = "response")

foodweb_glmer_TEST <- update(foodweb_glmer, .~. -Foodweb:I(sc.Diam^2) -Foodweb:I(sc.log.Clutch^2) -Foodweb:I(sc.log1p.Pref^2) -Foodweb:sc.Diam:sc.log.Clutch -Foodweb:sc.Diam:sc.log1p.Pref -Foodweb:sc.log.Clutch:sc.log1p.Pref)
vif.mer(foodweb_glmer_TEST)

# Evidence of nonlinear selection acting on gall size. No evidence of disruptive selection.
foodweb_glmer_2 <- update(foodweb_glmer, .~. -Foodweb:I(sc.Diam^2) -Foodweb:I(sc.log.Clutch^2) -Foodweb:I(sc.log1p.Pref^2) -Foodweb:sc.Diam:sc.log.Clutch:sc.log1p.Pref)
drop1(foodweb_glmer_2, test="Chisq") 
summary(foodweb_glmer_2)
visreg::visreg(foodweb_glmer_2, xvar="sc.Diam", scale = "response")

# Evidence of food-web treatment altering directional selection on clutch size; marginal evidence of correlational selection acting on gall size and clutch size.
foodweb_glmer_3 <- update(foodweb_glmer_2, .~. -I(sc.Diam^2) -I(sc.log.Clutch^2) -I(sc.log1p.Pref^2) -sc.Diam:sc.log.Clutch:sc.log1p.Pref -Foodweb:sc.Diam:sc.log.Clutch -Foodweb:sc.Diam:sc.log1p.Pref -Foodweb:sc.log.Clutch:sc.log1p.Pref)
drop1(foodweb_glmer_3, test="Chisq") 
summary(foodweb_glmer_3)
visreg::visreg(foodweb_glmer_3, xvar="sc.log.Clutch", by="Foodweb", scale="response")
visreg::visreg(foodweb_glmer_3, xvar="sc.Diam", by="sc.log.Clutch", scale="response")
visreg::visreg(foodweb_glmer_3, xvar="sc.log.Clutch", by="sc.Diam", scale="response") # a different perspective

# Evidence that food-web treatment alters absolute fitness; evidence of directional selection acting on gall size; evidence of directional selection acting on female preference
foodweb_glmer_4 <- update(foodweb_glmer_3, .~. -sc.Diam:sc.log.Clutch -sc.Diam:sc.log1p.Pref -sc.log.Clutch:sc.log1p.Pref -Foodweb:sc.Diam -Foodweb:sc.log.Clutch -Foodweb:sc.log1p.Pref)
drop1(foodweb_glmer_4, test="Chisq") 
summary(foodweb_glmer_4)
visreg::visreg(foodweb_glmer_4, xvar="Foodweb", scale="response")
visreg::visreg(foodweb_glmer_4, xvar="sc.Diam", scale="response")
visreg::visreg(foodweb_glmer_4, xvar="sc.log1p.Pref", scale="response")
```

>>>>

## FIT GLMMs ---

# Null Model
null_glmer <- glmer(gall_survival ~ 1 +
                      (1|Genotype/Plant_Position/Gall_Number),
                    data = gall_selection.df,
                    family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))

# Model assuming no effect of food-web treatment
trait_glmer <- glmer(gall_survival ~ (sc.Diam + sc.log.Clutch + sc.log1p.Pref)^2 + 
                      I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.log1p.Pref^2) +
                      (1|Genotype/Plant_Position/Gall_Number),
                    data = gall_selection.df,
                    family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))

# Model allowing for an effect of food-web treatment
foodweb_glmer <- glmer(gall_survival ~ Foodweb*(sc.Diam + sc.log.Clutch + sc.log1p.Pref)^2 +
                         Foodweb*(I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.log1p.Pref^2)) +
                         (1|Genotype/Plant_Position/Gall_Number),
                       data = gall_selection.df,
                       family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))

## STATISTICAL TESTS ----

# There is clear evidence that the traits we have measured influence larva survival
anova(null_glmer, trait_glmer, test="Chisq")
rsquared(list(null_glmer, trait_glmer))

# There is also clear evidence that our food-web treatment altered natural selection
anova(trait_glmer, foodweb_glmer)
rsquared(list(trait_glmer, foodweb_glmer), method="delta") # 3-4% increase in amount of variance explained when including effect of food-web treatment

## EVALUATING MODEL ASSUMPTIONS ---

# There is no evidence of overdispersion
overdisp_fun(foodweb_glmer)

# There are no clear patterns in the distribution of the residuals (= good)
visreg(foodweb_glmer)

@@

# Overall, there is clear evidence that food-web treatment alters absolute fitness
anova(null_glmer, trait_glmer, foodweb_glmer, test = "Chisq") 
```
